Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-03-20 article.rnw
Simplify the sentence explaining phylogeny-based grouping.
The mention of Darwin added nothing in particular.

In ecological contexts, such groups have been defined \emph{a priori} by phylogeny at some taxonomic level or by functional groupings \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling}.
The argument for grouping based on phylogeny is based on the principle (originally hypothesised by Darwin himself \cite{XXX}) that closely related species will be similar in (what we now know as) ecological niche, and thereby will interact with other species in a similar fashion \parencite{godoy2014phylogenetic}.
% DBS: the preceding sentence could be simplified a fair bit
However, empirical tests of this principle have found remarkably little support for it \parencite{godoy2014phylogenetic,cahill2008does,mayfield2010opposing}.
On the other hand, functional groupings have also proven to be poor predictors of species interactions \parencite{bret2008plant}.
While attempts have been made to define functional groupings that are more useful in a modelling context \parencite{boulangeat2012improving}, these rely upon measurements of biotic interactions to define such groups.
As such, integrating these into species interaction models leaves us with a circular argument: a functional group is a group of species that interact with others in a similar way, and we therefore assume that all the species in a functional group interact with others in a similar way.
In all, we are left with the question of how best to group species in community models, and whether we can do so in a meaningful fashion with less data than required for a fully pairwise parameterisation.

>>>>

In ecological contexts, such groups have been defined \emph{a priori} by phylogeny at some taxonomic level or by functional groupings \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling}.
The argument for grouping based on phylogeny relies on the principle that closely related species will fill similar ecological niches, and hence will interact with other species in a similar fashion \parencite{godoy2014phylogenetic}.
However, empirical tests of this principle have found remarkably little support for it \parencite{godoy2014phylogenetic,cahill2008does,mayfield2010opposing}.
On the other hand, functional groupings have also proven to be poor predictors of species interactions \parencite{bret2008plant}.
While attempts have been made to define functional groupings that are more useful in a modelling context \parencite{boulangeat2012improving}, these rely upon measurements of biotic interactions to define such groups.
As such, integrating these into species interaction models leaves us with a circular argument: a functional group is a group of species that interact with others in a similar way, and we therefore assume that all the species in a functional group interact with others in a similar way.
In all, we are left with the question of how best to group species in community models, and whether we can do so in a meaningful fashion with less data than required for a fully pairwise parameterisation.
